\cvsection{Experience}

% Experienced with C (embedded systems), Java, Verilog, Labview, Git. Familiar with Python and Javascript.

\begin{cventries}

\cventry 
{Platform Intern}
{UpGuard}
{Mountain View, CA}
{Summer 2017}
{
\begin{cvitems}
\item {Worked as a Junior SRE using Kubernetes and Docker to support a front facing cyber security application.}
\item {Wrote modules for an internal app including communicating with the Pingdom API, creating custom API endpoints of my own, and writing activity logs to a PostgreSQL database based on user activity.}
\item {Developed a suite of shell tools to automate customer appliance upgrades, including a backup tool that saved an erroneous upgrade operation.}
\item {Designed 503 and 404 error pages and added them to the Nginx Ingress on Kubernetes clusters.}
\end{cvitems}
}
% \cventry
% {Software Dev Intern}
% {SFVision}
% {El Dorado Hills, CA}
% {Winter 2016}
% {
% \begin{cvitems}
% \item {Worked on an iOS app that uses the Salesforce API. Learned Objective C, the Salesforce API, and the iOS framework.}
% % \item {Conducted Objective C to Swift translation analysis and determined cost benefit analysis for our specific codebase and development team.}
% \item {Responsible for creating UX mockups and demos for version 3.0 release.}
% \end{cvitems}
% }
% \vspace{-2mm} % Reduce whitespace
\cventry
   {Assistant Project Manager}
   {rLoop Inc.}
   {Cameron Park, CA}
   {2015 - 2016}
   {
     \begin{cvitems}
       \item{Worked on the development of a nonprofit Hyperloop initiative.}
       \item {Managed over 100 team members in various subteams.}
       \item {Coordinated meetings and set up task management systems such as Redmine, Slack, Trello, and GitHub.}
%         \item {Contacted potential sponsors and created industry connections.}
       \item{Before promotion to Assistant Project Manager, worked on technical analysis and design.}
%        \item{Dealt with legal matters and 501(c)(3) registration.}
     \end{cvitems}
   }
      \cventry
    {Co-Founder \& CSO}
    {Pure Web Services}
    {Folsom, CA}
    {2015 - 2016}
    {
      \begin{cvitems}
        \item {Co-founded a web design agency to build capital for personal projects.}
        \item {Created and launched marketing campaigns.}
%         \item{Interacted with clients and walked them through onboarding process}
%         \item {Designed and built websites to client specifications.}
%         \item{Implemented systems for website design and construction, billing, client communication, etc.}
      \end{cvitems}
    } 
  \cventry
    {Manufacturing}
    {Sanders Aircraft Technology}
    {Ione, CA}
    {Summer 2014}
    {
      \begin{cvitems}
        \item{Manufacturing and assembly of aircraft smoke generators for international customers.}
        \item{Produced high precision components using metal press, CNC, lathe, pipe bending, and other machine shop tools.}
        \item{Worked on assembly from start to finish of smoke generators, including testing.}
%         \item{Learned about precision manufacturing, the aeronautics industry, and working with international clients.}
      \end{cvitems}
    }
  \cventry
    {Mechanical Design Lead}
    {FIRST Robotics Team 295}
    {Granite Bay, CA}
    {2010 - 2013}
    {
      \begin{cvitems}
        \item{Led multiple subteams to rapidly prototype robotic systems.}
        \item{Used Solidworks, CNCs, band saws, drill presses, metal lathes, and general hand tools.}
%         \item{Gave team presentations regarding design and mechanical decisions.}
        \item{Operated the robot in competition and collaborated with alliance partners.}
%         \item{Wrote grant proposal and gave presentation to H.B. Fuller which resulted in a \textbf{\$10,000 sponsorship.}}
      \end{cvitems} 
    }
%       \begin{cvsubentries}
%        \cvsubentry{}{SF Vision (iOS App Development Intern) }{Winter 2016}{}
% %        \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       \end{cvsubentries}
\end{cventries}
